### 2025-08-08 manuscript/manuscript.qmd
Introduction added a segment

>>>>

Academia suffers from issues regarding equity. A lack equity impacts productivity, innovation, and job satisfaction in the workplace, which hugely impact academic progress. One aspect of this inequity is that gender. Women are more at a disadvantage than men, with evidence suggesting that women are less present in positions of power, a pay gap remains between men and women in academia (16%) which is wider than other sectors (9%). In a “publish or perish” culture of science and academia (Kiai, 2019), one crucial aspect to focus on is authorship. The number and quality (e.g., journal reputation) of authorships an individual determines crucial career development such as grant funding and future (permanent) positions.
